---
output: rmarkdown::github_document
---

# aquarium

Validate 'Phishing' 'URLs' with the 'PhishTank' Service

## Description

'PhishTank' <www.phishtank.com> is a free community site where anyone can submit, 
verify, track and share 'phishing' data. Methods are provided to test if a 'URL' is classsified 
as a 'phishing' site and to download aggregated 'phishing' 'URL' databases.

## What's Inside The Tin

The following functions are implemented:

- `pt_check_url`:	Check an individual URL against PhishTank's database
- `pt_read_db`:	Retrieve a complete copy of the current PhishTank database

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/aquarium")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(aquarium)
library(hrbrthemes)
library(tidyverse)

# current verison
packageVersion("aquarium")

```

### Test a URL

```{r cache=TRUE}
x <- pt_check_url("http://www.seer.revpsi.org/hhh/1/")

x

glimpse(x)
```

### Get the databases

```{r cache=TRUE}
x <- pt_read_db(.progress = FALSE)

x

glimpse(x)
```

### Top Phishing Targets

```{r tgts, fig.width=9, fig.height=9, fig.retina=2}
filter(x, verified == "yes") %>% 
  count(day = as.Date(verification_time), target) -> targets

count(targets, target, sort=TRUE) %>%
  filter(target != "Other") %>% 
  head(9) -> top_named_targets

filter(targets, target %in% top_named_targets$target) %>% 
  mutate(target = factor(target, levels=rev(top_named_targets$target))) %>% 
  ggplot(aes(day, n, group=target, color=target)) +
  geom_segment(aes(xend=day, yend=0), size=0.25) +
  scale_x_date(name = NULL, limits=as.Date(c("2008-01-01", "2018-06-31"))) +
  scale_y_comma(name = "# entries/day") +
  ggthemes::scale_color_tableau() +
  facet_wrap(~target, scales="free") +
  labs(
    title = "PhishTank Top Phishing Targets 2008-present",
    subtitle = "Note: Free Y scale",
    caption = "Source: PhishTank <phishtank.com>"
  ) +
  theme_ipsum_rc(grid="Y", strip_text_face = "bold") +
  theme(legend.position="none")
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

